Learning Constraints and Optimization Criteria

### 2015-10-23 Paper.tex
Import Anton Background

\section{Background}
In this section a brief overview of the important concepts and relevant literature will be provided.

\paragraph{Clauses}
In order to reason about clauses, the standard notions of (function free) first-order logic are described.
An atom $p(t_1, t_2, ..., t_n)$ consists of a predicate symbol~$p$ that is applied to $n$ terms~$t_i$.
Terms are either constants or variables.
In this paper constants will be written in uppercase ($\mathit{John}$) and variables in lowercase ($\mathit{x}$).
A literal can be an atom $a$ (positive literal) or a negated atom $\lnot a$ (negative literal).
Clauses are disjunctions of literals $l_1 \lor l_2 \lor ... \lor l_k$ and are assumed to be universally quantified.
A clause can be expressed using a body and a head $\mathit{head} \leftarrow \mathit{body}$.
Hereby, positive literals are grouped in the head and negative literals are grouped in the body.
Sometimes clauses are also written as a set of literals $\{l_1, l_2, ..., l_k\}$.

@@

Related work \cite{campigotto2011active} has creates a weighted MAX-SAT problem by learning propositional clauses and weights using examples and absolute scores.
Inspired by their results, our research tries to learn first-order logic clauses and weights using examples and rankings.
The resulting optimization problem can be seen as an extension of weighted MAX-SAT in which the clauses are in first-order logic.

@@

ModelSeeker \cite{Beldiceanu:ModelSeeker} attempts to structure the problem variables in different ways.
The system then uses a large catalog of global constraints to to find the ones that hold within this structure. 
This approach allows for constraint learning from a few examples.

As mentioned earlier, the research of \cite{Lallouet:LearningCP} already tried to use ILP techniques to learn constraints.
In their approach, the search space of constraints is explored in a bidirectional manner, primarily using negative examples.

@@

% \paragraph{Logic Solver} " v ------ v   Dissolve"
% The logic system IDP \cite{de2013prototype,wittocx2008idp} is used to calculate whether examples satisfy clauses and is used as a theorem prover.
% It supports an extension of first-order logic ($FO(\cdot)$) and can also be used to generate new solutions.
% Background knowledge is given as an IDP theory.

>>>>

\section{Background}
In this section we provide a brief overview of the important concepts and relevant literature.

\paragraph{Clauses}
In order to reason about clauses, the standard notions of (function free) first-order logic are described.
An atom $p(t_1, t_2, ..., t_n)$ consists of a predicate symbol $p$ that is applied to $n$ terms $t_i$.
Terms are either constants or variables.
In this paper constants will be written in uppercase ($\mathit{John}$) and variables in lowercase ($\mathit{x}$).
A literal can be an atom $a$ (positive literal) or a negated atom $\lnot a$ (negative literal).
Clauses are disjunctions of literals $l_1 \lor l_2 \lor ... \lor l_k$ and are assumed to be universally quantified.
A clause can be expressed using a body and a head $\mathit{head} \leftarrow \mathit{body}$.
Hereby, positive literals are grouped in the head and negative literals are grouped in the body.
Sometimes clauses are also written as a set of literals $\{l_1, l_2, ..., l_k\}$.

@@

In related work \cite{campigotto2011active} a weighted MAX-SAT problem is created by learning propositional clauses and weights using examples and absolute scores.
Inspired by their results, our research tries to learn first-order logic clauses and weights using examples and rankings.
The resulting optimization problem can be seen as an extension of weighted MAX-SAT in which the clauses are in first-order logic.

@@

ModelSeeker \cite{Beldiceanu:ModelSeeker} attempts to structure the problem variables in different ways.
The system then uses a large catalog of global constraints to find the ones that hold within this structure. 
This approach allows for constraint learning from a few examples.

As mentioned earlier, the research of \cite{Lallouet:LearningCP} already tried to use ILP techniques to learn constraints.\anton{"tried to" sounds a bit negative}
In their approach, the search space of constraints is explored in a bidirectional manner, primarily using negative examples.

@@
